\documentclass[a4paper,10pt]{article}

\usepackage[lmargin=2.5cm,rmargin=2.5cm,tmargin=2.5cm,bmargin=2.5cm]{geometry}
\usepackage{titling}

% commands
\newcommand{\subtitle}[1]{%
    \posttitle{%
        \par\end{center}
        \begin{center}\large#1\end{center}
        \vskip0.5em }%
}

\begin{document}
\title{INFO3402}
\subtitle{Lecture Notes}
\date{Semester 1 - 2015}
\author{Scott Greenup}
\maketitle

\section{Administration Information}
\begin{itemize}
    \item bernard.wong@sydney.edu.au
    \item Assignment due dates:
    \begin{itemize}
        \item Assignment 1 in Week 5
        \item Assignment 2 in Week 8
        \item Assignment 3 Part 1 in Week 9
        \item Assignment 3 Part 2 in Week 10
        \item Assignment 3 Part 3 in Week 11
        \item Assignment 3 Part 4 in Week 12
    \end{itemize}
    \item Assignment hand-in process:
    \begin{itemize}
        \item A hard copy is handed in on the Tueday tutorial.
        \item A soft copy is handed in on the Monday night before the tutorial.
    \end{itemize}
    \item Assignment groups come out of the tutorials, and are of size 3-5.
    \item Assignments are marked as a group, you can ask for individual marking.
    \item Assignment is a case study.
    \item Assignments will teach about the "unwritten requirements" and the "left-field requirements".
    \item Tutorials are accessed via the backdoor of Madsen Building.
    \item Textbook = Information Technology Project Management 7th Edition
\end{itemize}

\section{Lecture 01 - 6th of March 2015}
\subsection{The Doctor's Insight}
\begin{itemize}
    \item The world is constantly changing, businesses constantly change.
    \item Trust needs to be built for a Project Manager to be effective.
    \item "You are dealing with people in today's day and age." - Dr. Benard Wong
    \item Managing emotions of teams is also a massive part of Project Management
    \item Product Management is a Project Management in terms of 'offerings'
    \item Projects is the vehicle to make money.
    \item The process of a startup will be impartially view upon.
    \item When a project fails, the impact... someone could die from this.
    \item You can never test everything!
    \item The project management is there to sheild the contractor, and the team.
\end{itemize}

\subsection{Notes}
\begin{itemize}
    \item No silver bullet approach. Project Management is to complicated.
    \item A project should be well defined, and needs to be planned appropriately.
    \item Creation, planning, and scheduling => on-going management => communication and reporting
\end{itemize}
\end{document}
